Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-10 doc/paper.tex
adds more results

@@

\textbf{Contrastive Learning in 3D}
DepthContrast \cite{zhang2021Self}

@@

            PointContrast \cite{xie2020pointcontrast}           & Pair & $>$ 70\% & 46.1 \textbf{(+3.9)}                               & 50.7 (-0.4)                                           & 58.0 (-0.2)          & 61.9 \textbf{(+2.7)} & 62.6 \textbf{(+0.4)} & 67.3 (-0.1)           & 28.0 \textbf{(+1.1)} & 35.7 (-0.6)          & 40.5 (-0.2)          & 42.8 \textbf{(+0.6)} & 44.4 (-1.3) & --                   \\
            PointContrast \cite{xie2020pointcontrast}           & Same & --       & 45.5 \textbf{(+3.3)}                               & 48.8 (-2.3)                                           & 56.7 (-1.5)          & 59.3 \textbf{(+0.1)} & 61.7 (-0.5)          & 66.5 (-0.9)           & --                   & --                   & --                   & --                   & --          & --                   \\

@@

            CSC \cite{hou2021Exploring}                         & Pair & $>$ 70\% & 45.4 \textbf{(+3.2)}                               & 50.8 (-0.3)                                           & 59.3 \textbf{(+1.1)} & 59.7 \textbf{(+0.5)} & 62.7 \textbf{(+0.5)} & 68.0 \textbf{(+0.6)}  & 29.8 \textbf{(+2.9)} & 37.6 \textbf{(+1.3)} & 41.4 \textbf{(+0.7)} & --                   & --          & --                   \\
            CSC \cite{hou2021Exploring}                         & Same & --       & 44.1 \textbf{(+1.9)}                               & 50.9 (-0.2)                                           & 56.6 (-1.6)          & 58.9 (-0.3)          & 61.5 (-0.7)          & 67.4 \textbf{(+0.0)}  & 28.8 \textbf{(+1.9)} & 37.2 \textbf{(+0.9)} & 42.0 \textbf{(+1.3)} & --                   & --          & --                   \\

>>>>

DenseCL \cite{wang_dense_2021} Does contrastive learning at the pixel level of images giving a good background into extracting image level features.

@@

\textbf{Contrastive Learning in 3D}
DepthContrast \cite{zhang2021Self}, PointContrast \cite{xie2020pointcontrast}, Contrastive scene contexts \cite{hou2021Exploring}

Occlusion completion \cite{wang_unsupervised_nodate}

@@

            PointContrast \cite{xie2020pointcontrast}           & Pair & $>$ 70\% & 46.1 \textbf{(+3.9)}                               & 50.7 (-0.4)                                           & 58.0 (-0.2)          & 61.9 \textbf{(+2.7)} & 62.6 \textbf{(+0.4)} & 67.3 (-0.1)           & 28.0 \textbf{(+1.1)} & 35.7 (-0.6)          & 40.5 (-0.2)          & 42.8 \textbf{(+0.6)} & 44.4 (-1.3)          & 48.4 (-0.6)          \\
            PointContrast \cite{xie2020pointcontrast}           & Same & --       & 45.5 \textbf{(+3.3)}                               & 48.8 (-2.3)                                           & 56.7 (-1.5)          & 59.3 \textbf{(+0.1)} & 61.7 (-0.5)          & 66.5 (-0.9)           & 27.9 \textbf{(+1.0)} & 36.0 (-0.3)          & 36.6 (-3.4)          & 43.5 \textbf{(+1.3)} & 44.5 (-1.2)          & 48.5 (-0.5)          \\

@@

            CSC \cite{hou2021Exploring}                         & Pair & $>$ 70\% & 45.4 \textbf{(+3.2)}                               & 50.8 (-0.3)                                           & 59.3 \textbf{(+1.1)} & 59.7 \textbf{(+0.5)} & 62.7 \textbf{(+0.5)} & 68.0 \textbf{(+0.6)}  & 29.8 \textbf{(+2.9)} & 37.6 \textbf{(+1.3)} & 41.4 \textbf{(+0.7)} & 43.9 \textbf{(+1.7)} & 47.3 \textbf{(+1.6)} & 48.7 (-0.3)          \\
            CSC \cite{hou2021Exploring}                         & Same & --       & 44.1 \textbf{(+1.9)}                               & 50.9 (-0.2)                                           & 56.6 (-1.6)          & 58.9 (-0.3)          & 61.5 (-0.7)          & 67.4 \textbf{(+0.0)}  & 28.8 \textbf{(+1.9)} & 37.2 \textbf{(+0.9)} & 42.0 \textbf{(+1.3)} & 43.8 \textbf{(+1.6)} & 44.5 (-0.2)          & 48.5 (-0.5)          \\
